### 2009-10-25 doc/manuals/user_interface/ui-data.tex
arcsync, arcsub and chelonia fixed

>>>>

\subsection{chelonia}\label{sec:chelonia}

\index{chelonia}\index{commands:chelonia}\texttt{chelonia} is a client tool for
accessing the Chelonia storage system. With it you can
create, remove and list file collections, upload, download and remove files,
and move and stat collections and files, using Logical Names (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia [options] $<$method$>$ [arguments]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-b} & \textit{URL} & URL of Bartender to connect\\
   \texttt{-x} && print SOAP XML messages\\
   \texttt{-v} && verbose mode\\
   \texttt{-z}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-w} && allow to run without the ARC python client libraries (with limited functionality)\\
   Methods:&&\\
   \texttt{stat} &\textit{LN [LN ...]}& get detailed information about an entry or several\\
   \texttt{makeCollection, make, mkdir} &\textit{LN}& create a collection\\
   \texttt{unmakeCollection, unmake, rmdir} &\textit{LN}& remove an empty collection\\
   \texttt{list, ls} &\textit{LN}& list the content of a collection\\
   \texttt{move, mv} &\textit{source target}& move entries within the namespace (both LNs)\\
   \texttt{putFile, put} &\textit{source target}& upload a file from a \textit{source} to a \textit{target} (both specified as LNs))\\
   \texttt{getFile, get} &\textit{source [target]}& download a file from a \textit{source} to a \textit{target}\\
   \texttt{delFile, del, rm} &\textit{LN [LN ...]}& remove file(s))\\
   \texttt{modify, mod} &\textit{string}& modify metadata\\
   \texttt{policy, pol} &\textit{string}& modify access policy rules. The string has a form $<$LN$>$ $<$changeType$>$ $<$identity$>$ $<$action list$>$.\\
   & &$<$changeType$>$ could be 'set', 'change' or 'clear'\\
   & & 'set': sets the action list to the given user overwriting the old one\\
   & & 'change': modify the current action list with adding and removing actions\\
   & & 'clear': clear the action list of the given user\\
   & &$<$identity$>$ could be a '$<$UserDN$>$' or a 'VOMS:$<$VO name$>$'\\
   & &$<$action list$>$ is a list actions prefixed with '+' or '-', e.g. '+read +addEntry -delete'; possible actions are: \texttt{read}, \texttt{addEntry}, \texttt{removeEntry}, \texttt{delete}, \texttt{modifyPolicy}, \texttt{modifyStates}, \texttt{modifyMetadata}\\
   \texttt{unlink} &\textit{string}& remove a link to an entry from a collection without removing the entry itself\\
   \texttt{credentialsDelegation, cre} &\textit{string}& delegate credentials for using gateway\\
   \texttt{removeCredentials, rem} &\textit{string}& remove previously delegated credentials\\
   \texttt{makeMountPoint, makemount} &\textit{string}& create a mount point\\
\end{longtable}

Without arguments, each method prints its own help.

Examples:
\begin{verbatim}
    chelonia list /
    chelonia put orange /
    chelonia stat /orange
    chelonia get /orange /tmp
    chelonia mkdir /fruits
    chelonia mkdir /fruits/apple
    chelonia mv /orange /fruits
    chelonia ls /fruits
    chelonia rmdir /fruits/apple
    chelonia rmdir /fruits
    chelonia rm /fruits/orange
    chelonia policy / change ALL +read +addEntry
    chelonia modify /pennys-orange set states neededReplicas 2
\end{verbatim}

### 2009-10-25 doc/manuals/user_interface/ui-job.tex
arcsync, arcsub and chelonia fixed

\subsection{arcsub}\label{sec:arcsub}
The \texttt{arcsub}\index{arcsub}\index{commands:arcsub} command is the
most essential one, as it is used for submitting jobs to the Grid
resources. \index{submit job}. \texttt{arcsub} matches user's job
description to the information collected from the Grid, and the
optimal site is being selected for job submission. The job description
is then being forwarded to that site, in order to be submitted to the
Local Resource Management System (LRMS), which can be, e.g., PBS or
Condor or SGE etc.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options]}%$<$task ...$>$
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject a specific site (cluster)\\
   \texttt{-i, --indexurl}&\textit{url}&URL of an index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where the job IDs will be stored\\
   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{time}&timeout for queries in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
%   Arguments:&&\\
%   \texttt{ task ...}&&strings or files describing the jobs to be submitted\\
\end{longtable}

\begin{framed}
The -c and -i arguments accept ``urls'' of the format GRID:URL,

e.g. for index servers:

ARC0:ldap://grid.tsl.uu.se:2135/mds-vo-name=sweden,O=grid

CREAM:ldap://cream.grid.upjs.sk:2170/o=grid

or clusters:

ARC0:ldap://grid.tsl.uu.se:2135/nordugrid-cluster-name=grid.tsl.uu.se,Mds-Vo-name=local,o=grid
\end{framed}

@@

\begin{shaded}
\uicommand{arcsub -c ARC0:ldap://grid.tsl.uu.se:2135/nordugrid-cluster-name=grid.tsl.uu.se,Mds-Vo-name=local,o=grid -f job.jsdl}
\end{shaded}

Assuming that the url represents an ARC0 cluster that the user is authorized to submit to and job.jsdl is the file below.

@@

@@

% \subsection{arcrenew}
% \label{sec:arcrenew}
% 
% Quite often, the user proxy expires while the job is still running (or
% waiting in a queue). In case such job has to upload output files to a
% Grid location (Storage Element), it will fail. By using the \texttt{arcrenew}
% \index{arcrenew}\index{commands:arcrenew} command, users can upload
% a new proxy to the job. This can be done while a job is still running,
% thus preventing it from failing, or whithin 24 hours (or whatever is
% the expiration time set by the site) after the job
% end. In the latter case, the Grid Manager will attempt to finalize
% the job by uploading the output files to the desired location.
% 
% \hspace*{0.5cm}
% \begin{shaded}
%    \uicommand{arcrenew [options] [job ...]}
% \end{shaded}
% \versions{ARC 0.9}
% \begin{longtable}{llp{8cm}}
%    Options:&&\\
%    \texttt{-a, -all}& & all jobs\\
%    \texttt{-i, -joblist}& \textit{filename} & file containing a list of jobIDs\\
%    \texttt{-c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
%    \texttt{-C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
%    \texttt{-s, -status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%    \texttt{-t, -timeout}& \textit{time} & timeout for queries (default 40 sec)\\
%    \texttt{-d, -debug}& \textit{debuglevel} &debug level, from -3 (quiet) to 3 (verbose) - default 0\\
%    \texttt{-x, -anonymous}& & use anonymous bind for queries (default)\\
%    \texttt{-X, -gsi}& & use GSI-GSSAPI bind for queries\\
%    \texttt{-v, -version}& & print version information\\
%    \texttt{-h, -help}& & print help page\\
%    Arguments:&&\\
%    \texttt{job ...} && list of job IDs and/or jobnames\\
% \end{longtable}
% 
% Prior to using \texttt{arcrenew}, be sure to actually create the
% new proxy!
% 
% \subsection{arcsync}
% \label{sec:arcsync}
% 
% If you are using User Interface installations on different machines,
% your local lists of submitted jobs will be different. To synchronise
% these lists with the information in the Information System, use the
% \texttt{arcsync} \index{arcsync}\index{commands:arcsync} command.
% 
% \hspace*{0.5cm}
% \begin{shaded}
%    \uicommand{arcsync [options]}
% \end{shaded}
% \versions{ARC 0.9}
% \begin{longtable}{llp{8cm}}
%    Options:&&\\
%    \texttt{-c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
%    \texttt{-C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
%    \texttt{-g, -giisurl}& \textit{url} &URL of a central Information System server\\
%    \texttt{-G, -giislist}&\textit{filename}&list of GIIS URLs\\
%    \texttt{-f, -force}&&don't ask for confirmation\\
%    \texttt{-t, -timeout}& \textit{time} & timeout for queries (default 40 sec)\\
%    \texttt{-d, -debug}& \textit{debuglevel} &debug level, from -3 (quiet) to 3 (verbose) - default 0\\
%    \texttt{-x, -anonymous}& & use anonymous bind for queries (default)\\
%    \texttt{-X, -gsi}& & use GSI-GSSAPI bind for queries\\
%    \texttt{-v, -version}& & print version information\\
%    \texttt{-h, -help}& & print help page\\
% \end{longtable}
% 
% The ARC User Interface keeps a local list of jobs in the user's home
% directory (see section~\ref{sec:joblists}). If this file is lost,
% corrupt, or the user wants to recreate the file on a different
% workstation, the \texttt{arcsync} command will recreate this file from
% the information available in the Information System.

>>>>

\subsection{arcsync}
\label{sec:arcsync}

It is advised to start every grid session by running \texttt{arcsync},
especially when changing workstations. The reason is that your job submission
history is cached on your machine, and if you are using ARC client
installations on different machines, your local lists of submitted jobs will be different. To synchronise
these lists with the information in the Information System, use the
\texttt{arcsync} \index{arcsync}\index{commands:arcsync} command.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsync [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
   \texttt{-f, --force}& &don't ask for confirmation\\
%   \texttt{-m, --merge}& &merge the found jobs with the jobs already in the joblist\\
   \texttt{-T, --truncate}& &truncate the job list before synchronising\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
\end{longtable}

The ARC client keeps a local list of jobs in the user's home
directory. If this file is lost,
corrupt, or the user wants to recreate the file on a different
workstation, the \texttt{arcsync} command will recreate this file from
the information available in the Information System.

Since  the  information  about  a job retrieved from a clsuter can be slightly out of date if the user very recently
submitted or removed a job, a warning is issued when this command is run. The \verb#--force# option disables this warning.

%If a specific cluster is selected for the syncronisation while the job list contains jobs  on  a  different  cluster,
%running  the arcsync command will remove the old jobs from the joblist, unless the \verb#--merge# option is given, in which
%case the new found jobs are merged with the jobs already in the joblist.

\subsection{arcsub}\label{sec:arcsub}
The \texttt{arcsub}\index{arcsub}\index{commands:arcsub} command is the
most essential one, as it is used for submitting jobs to the Grid
resources. \index{submit job}\texttt{arcsub} matches user's job
description to the information collected from the Grid, and the
optimal site is being selected for job submission. The job description
is then being forwarded to that site, in order to be submitted to the
Local Resource Management System (LRMS), which can be, e.g., PBS or
Condor or SGE etc.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] [filename]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
%   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
%   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-b, --broker}&\textit{string}&select broker method (default is Random)\\
   \texttt{-n, --dolocalsandbox}& &store job descriptions in local sandbox (useful for eventual resubmission/migration)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
   Arguments:&&\\
   \texttt{filename}&&file describing the job(s) to be submitted\\
\end{longtable}

\begin{framed}
The \verb#-c# and \verb#-i# arguments accept meta-URLs of the format \texttt{GRID:URL}, where \texttt{GRID} indicates a Grid middleware flavour. Possible flavours are \texttt{ARC0}, \texttt{ARC1}, \texttt{CREAM} and \texttt{UNICORE}. For example, for index servers:
\begin{verbatim}
 ARC0:ldap://index.ng.org:2135/mds-vo-name=sweden,O=grid
 CREAM:ldap://cream.glite.org:2170/o=grid
\end{verbatim}
or clusters:

\verb# ARC0:ldap://ce.ng.eu:2135/nordugrid-cluster-name=ce.ng.eu,Mds-Vo-name=local,o=grid#
\end{framed}

@@

\begin{shaded}
 arcsub -c ARC0:ldap://grid.ng.org:2135/nordugrid-cluster-name=grid.ng.org,Mds-Vo-name=local,o=grid -f job.jsdl
\end{shaded}

A user has to have valid credentials (see Section~\ref{sec:proxy}) and be authorised at the specified site. The test file \texttt{job.jsdl} is shown below.

@@

\begin{framed}
   If a job is successfully submitted, a \textbf{job identifier}
   (\textit{job ID})\index{job ID} is printed to standard output.
\end{framed}

The job ID uniquely identifies the job while it is being executed. Job IDs
differ strongly between Grid flavours, but basically they have a form of a URL.
You should use Job ID as a handle to refer to the job when doing other
job manipulations, such as querying job status (\verb#arcstat#),
killing it (\verb#arckill#), re-submitting (\verb#arcresub#), or
retrieving the result (\verb#arcget#).

\begin{framed}
   Every job ID is a valid URL for the job session directory. You can
   always use it to access the files related to the job, by using data
   management tools (see Chapter~\ref{sec:dm}).
\end{framed}

The job description in xRSL or JSDL format can be given either as an
argument on the command line, or can be read from a file. Several jobs can be
requested at the same time by giving more than one filename
argument, or by repeating the \verb#-f# or \verb#-e# options. It is
possible to mix \verb#-e# and \verb#-f# options in the same
\texttt{arcsub} command.

The \verb#-c# option can be used to \textbf{force} a job to be
submitted to a particular site (cluster), or to reject submission to a
site. The matching is done by string match to the site name (i.e.
hostname) as defined in the Information System, or to an alias, as
defined in user configuration file (see
Section~\ref{sec:client.conf}).  The \verb#-c# option can be repeated
several times, for example:
\begin{verbatim}
    arcsub -c alias1 -c alias2 myjob.xrsl
\end{verbatim}
This will submit a job to either \verb#alias1# or
\verb#alias2#. To submit a job to any site except
\verb#badsite#, use \verb#-# sign in front of the name:
\begin{verbatim}
    arcsub -c -badsite myjob.xrsl
\end{verbatim}

If option \verb#-c# is not given, the \verb#arcsub# command locates the available sites by querying the
Information System. Default index services for the Information System are specified in the
configuration template distributed with the middleware, and can be overwritten both in the user's
configuration (see Section~\ref{sec:client.conf}) and from the command line using option
\verb#-i#. Different Grids use different notation for such index services.

If you would like to get diagnostics of the process of resource
discovery and requirements matching, a very useful option is
\verb#-d#. The following command:
\begin{verbatim}
    arcsub -d DEBUG myjob.xrsl
\end{verbatim}

will print out the steps taken by the ARC client to find the
best cluster satisfying your job requirements. A default value for
the debug level can be set in the user's configuration file.

It often happens that some sites that \verb#arcsub# has to contact
are slow to answer, or are down altogether. This will not prevent
you from submitting a job, but will slow down the submission. To
speed it up, you may want to specify a shorter timeout (default is
20 seconds) with the \verb#-t# option:
\begin{verbatim}
    arcsub -t 5 myjob.xrsl
\end{verbatim}

A default value for the timeout can be set in the user's configuration file.

The user interface transforms input job description into a format
that can be understood by the Grid services to which it is being
submitted. By specifying the \verb#-dumpdescription# option, such transformed
description is written to stdout instead of being submitted to the remote site.

Possible broker values for the option \verb#-b# are:
\begin{itemize}
 \item[\texttt{Random}] -- ranks targets randomly (default)
 \item[\texttt{FastestQueue}] -- ranks targets according to their queue length
% \item[\texttt{FastestCPU}] -- ranks targets according to CPU performance
 \item[\texttt{Data}] -- ranks target according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
% \item[\texttt{SampleBroker}] -- Ranks targets randomly (written in Python)
\end{itemize}

@@

% \subsection{arcrenew}
% \label{sec:arcrenew}
% 
% Quite often, the user proxy expires while the job is still running (or
% waiting in a queue). In case such job has to upload output files to a
% Grid location (Storage Element), it will fail. By using the \texttt{arcrenew}
% \index{arcrenew}\index{commands:arcrenew} command, users can upload
% a new proxy to the job. This can be done while a job is still running,
% thus preventing it from failing, or whithin 24 hours (or whatever is
% the expiration time set by the site) after the job
% end. In the latter case, the Grid Manager will attempt to finalize
% the job by uploading the output files to the desired location.
% 
% \hspace*{0.5cm}
% \begin{shaded}
%    \uicommand{arcrenew [options] [job ...]}
% \end{shaded}
% \versions{ARC 0.9}
% \begin{longtable}{llp{8cm}}
%    Options:&&\\
%    \texttt{-a, -all}& & all jobs\\
%    \texttt{-i, -joblist}& \textit{filename} & file containing a list of jobIDs\\
%    \texttt{-c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
%    \texttt{-C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
%    \texttt{-s, -status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%    \texttt{-t, -timeout}& \textit{time} & timeout for queries (default 40 sec)\\
%    \texttt{-d, -debug}& \textit{debuglevel} &debug level, from -3 (quiet) to 3 (verbose) - default 0\\
%    \texttt{-x, -anonymous}& & use anonymous bind for queries (default)\\
%    \texttt{-X, -gsi}& & use GSI-GSSAPI bind for queries\\
%    \texttt{-v, -version}& & print version information\\
%    \texttt{-h, -help}& & print help page\\
%    Arguments:&&\\
%    \texttt{job ...} && list of job IDs and/or jobnames\\
% \end{longtable}
% 
% Prior to using \texttt{arcrenew}, be sure to actually create the
% new proxy!
%
